---
title: "CodeBook"
output: html_document
---

The function *run_analysis()* contained in **run_analysis.R** returns a list containing two data sets: 

- full_data
- summarized_data

```{r}
source('~/Documents/DataScienceTrack/UCI HAR Dataset/run_analysis.R', encoding = 'UTF-8')
results <- run_analysis()
summary(results)
```

The script combines the *Y* test/train data and *Subject* test/train to the *X* test/train data (respectfully).  Then the joined *train* data set is unioned with the *test* data set.  The activity idenification numbers are replaced with the activity name.  Features listed in *feature.txt* are matched to the appropriate column and used as the column name.  Only features with "[Mm]ean" or "[Ss]td" in the text string were kept in the data set.

There are 88 columns in each data set.  The first column is the subject idenitifcation number and the second column is the observed activity.  The remaining 86 columns in the **full_data** data set represent the mean or standard deviation dervived while observing the subject doing the activity for a single observation.  The remaining 86 columns in the **summarized_data** data set represent the average of all of that subject’s observations doing that activity.

```{r}
colnames(results$full_data)
```
